What is an Ancestral Recombination Graph?

### 2022-02-13 paper.tex
Text for pedigree-based model

\section*{Introduction}
Inferring the genetic relationships between sampled genomes in the form of an
evolutionary tree is a necessary prerequisite for many analyses of species \citep{rannala2003genetics}, non (or
rarely) recombining sections of DNA \citep{cann1987mitochondrial,underhill2001annalsofhumangenetics} and viruses \citep{grenfell2004science}.
A genealogical tree captures what is known and
knowable about the genetic ancestry of the sample in an elegant and concise
way, by postulating a set of nodes that are ancestors common to the samples,
and the ancestral relationships between those nodes. A rich literature exists
on analysing the mathematical properties of these trees [cite?], and numerous
methods exist to infer them~\citep{felsenstein2004inferring}. The situation is
quite different in recombining organisms, where the analysis of genetic data
depends on summaries ultimately derived from the
trees~\citep{tajima1983evolutionary,tavare1984line,fu1995statistical}
such as allele frequencies and site frequency
spectra~\citep{achaz2009frequency,ralph2020efficiently},
patterns of linkage disequilibrium~\citep{mcvean2002genealogical}, and principal
components~\citep{mcvean2009genealogical}. Genealogical analysis is equally
fundamental to the study of recombining organisms, but profound technical
difficulties have made the routine inference of recombinant genealogies
impossible, and therefore tree-based analysis methods have been largely
unavailable to the fields of population and statistical
genetics.

@@

In this paper we [turn into proper round up paragraph later]
\begin{enumerate}
\item Discuss the classical Ancestral Recombination Graph formulation,
and show how it derives from (and is limited by) the coalescent with
recombination.
\item Suggest a definition of ARGs that is free of these limitations,
where the formulation is derived from a (normally diploid) pedigree rather than from
coalescent approximations, and where the genetic
material which is transmitted is described by annotations attached to
edges rather than nodes.
\item Suggest a classification of ARG nodes that helps us to understand
the properties of the structures inferred by different methods, and illustrate
with some examples.
\end{enumerate}

@@

\begin{figure}[ht]
\centering
% FIXME this is a quick nasty hack to make the figure a bit smaller and
% prevent flushing all the other figures to the end of the document.
\scalebox{0.5}{
\begin{tabular}{cc}
\begin{tikzpicture}
	% Samples at x = 0, 4, and 6
	\node [circle, fill, scale=0.2,label=above right:{\small A}] at (0,0) {A};
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\node [circle, fill, scale=0.2,label=above right:{\small B}] at (4,0) {B};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\node [circle, fill, scale=0.2,label=above left:{\small C}] at (6,0) {C};
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);

	% B and C merge into D
	\draw (4,0) -- (4, 1.2) -- (6, 1.2) -- (6,0);
	\node [circle, fill, scale=0.2,label=above right:{\small D}] at (5,1.2) {D};
	\draw (4.6, 1) -- (5.4, 1) -- (5.4, 0.9) -- (4.6, 0.9) -- (4.6, 1);
	\draw (5.1, 1.1) -- (5.1, 0.8);
	\node [label=below:{\small $w$}] at (5.1, 1) {};

	% A splits into E and F
	\draw (0, 0) -- (0, 1.5) -- (-1,1.5) -- (1,1.5);
	\node [circle, fill, scale=0.2,label=above left:{\small E}] at (-1,1.5) {E};
	\draw (-1.4, 1.3) -- (-1.1, 1.3) -- (-1.1, 1.2) -- (-1.4, 1.2) -- (-1.4, 1.3);
	\draw (-1.1, 1.25) -- (-0.6, 1.25);
	\node [circle, fill, scale=0.2,label=above left:{\small F}] at (1,1.5) {F};
	\draw (0.6, 1.25) -- (0.9, 1.25);
	\draw (0.9, 1.3) -- (1.4, 1.3) -- (1.4, 1.2) -- (0.9, 1.2) -- (0.9, 1.3);
	\draw (1.2, 1.4) -- (1.2, 1.1);
	\node [label=below:{\small $x$}] at (1.2, 1.3) {};

	% D splits into G and H
	\draw (5, 1.2) -- (5, 2.4) -- (4,2.4) -- (6,2.4);
	\node [circle, fill, scale=0.2,label=above left:{\small G}] at (4,2.4) {G};
	\draw (3.6, 2.2) -- (4.1, 2.2) -- (4.1, 2.1) -- (3.6, 2.1) -- (3.6, 2.2);
	\draw (4.1, 2.15) -- (4.4, 2.15);
	\node [circle, fill, scale=0.2,label=above left:{\small H}] at (6,2.4) {H};
	\draw (5.6, 2.15) -- (6.1, 2.15);
	\draw (6.1, 2.2) -- (6.4, 2.2) -- (6.4, 2.1) -- (6.1, 2.1) -- (6.1, 2.2);

	% F splits into I and J
	\draw (1, 1.5) -- (1, 3.1) -- (0,3.1) -- (2,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small I}] at (0,3.1) {I};
	\draw (-0.4, 2.85) -- (0.2, 2.85);
	\draw (0.2, 2.9) -- (0.4, 2.9) -- (0.4, 2.8) -- (0.2, 2.8) -- (0.2, 2.9);
	\node [circle, fill, scale=0.2,label=above left:{\small J}] at (2,3.1) {J};
	\draw (1.6, 2.85) -- (1.9, 2.85);
	\draw (1.9, 2.9) -- (2.2, 2.9) -- (2.2, 2.8) -- (1.9, 2.8) -- (1.9, 2.9);
	\draw (2.2, 2.85) -- (2.4, 2.85);

	% E and I merge into K
	\draw (-1, 1.5) -- (-1, 4.5) -- (0,4.5) -- (0,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small K}] at (-0.5,4.5) {K};
	\draw (-0.9, 4.3) -- (-0.6, 4.3) -- (-0.6, 4.2) -- (-0.9, 4.2) -- (-0.9, 4.3);
	\draw (-0.6, 4.25) -- (-0.3, 4.25);
	\draw (-0.3, 4.3) -- (-0.1, 4.3) -- (-0.1, 4.2) -- (-0.3, 4.2) -- (-0.3, 4.3);
	\draw (-0.5, 4.4) -- (-0.5, 4.1);
	\node [label=below:{\small $y$}] at (-0.5, 4.3) {};

	% G and J merge into L
	\draw (4,2.4) -- (4,5.4) -- (2,5.4) -- (2,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small L}] at (3,5.4) {L};
	\draw (2.6, 5.2) -- (2.9, 5.2) -- (2.9, 5.1) -- (2.6, 5.1) -- (2.6, 5.2);
	\draw (2.9, 5.15) -- (3.4, 5.15);

	% K splits into M and N
	\draw (-0.5, 4.5) -- (-0.5, 6) -- (-1.5,6) -- (0.5,6);
	\node [circle, fill, scale=0.2,label=above left:{\small M}] at (-1.5,6) {M};
	\draw (-1.9, 5.75) -- (-1.3, 5.75);
	\draw (-1.3, 5.8) -- (-1.1, 5.8) -- (-1.1, 5.7) -- (-1.3, 5.7) -- (-1.3, 5.8);
	\node [circle, fill, scale=0.2,label=above left:{\small N}] at (0.5,6) {N};
	\draw (0.1, 5.8) -- (0.4, 5.8) -- (0.4, 5.7) -- (0.1, 5.7) -- (0.1, 5.8);
	\draw (0.4, 5.75) -- (0.9, 5.75);

	% L and N merge into O
	\draw (0.5, 6) -- (0.5, 7.2) -- (3,7.2) -- (3,5.4);
	\node [circle, fill, scale=0.2,label=above left:{\small O}] at (1.75,7.2) {O};
	\draw (1.35, 6.95) -- (2.15, 6.95);

	% M and H continue to the end
	\draw (-1.5, 6) -- (-1.5, 8);
	\draw (6, 2.4) -- (6, 8);

	% Edge annotations above each node
	\node [label=left:{\small$\{[0,L)\};1$}] at (0.2,0.6) {}; % A
	\node [label=left:{\small$\{[0,L)\};1$}] at (4.2,0.4) {}; % B
	\node [label=right:{\small$\{[0,L)\};1$}] at (5.8,0.4) {}; % C
	\node [label=left:{\small$\{[0,L)\};2$}] at (5.2,1.6) {}; % D
	\node [label=left:{\small$\{[0,v)\};1$}] at (-0.8,2.3) {}; % E
	\node [label=right:{\small$\{[v,L)\};1$}] at (0.8,2.1) {}; % F
	\node [label=right:{\small$\{[0,w)\};2$}] at (3.8,3.9) {}; % G
	\node [label=left:{\small$\{[w,L)\};2$}] at (6.2,5) {}; % H
	\node [label=right:{\small$\{[x,L)\};1$}] at (-0.2,3.8) {}; % I
	\node [label=right:{\small$\{[v,x)\};1$}] at (1.8,4.1) {}; % J
	\node [label=left:{\small$\{[0,v), [x, L)\};1$}] at (-0.3,5.2) {}; % K
	\node [label=right:{\small$\{[0,v)\};2$}] at (2.8,6.4) {}; % L
	\node [label=left:{\small$\{[x,L)\};1$}] at (-1.3,7) {}; % M
	\node [label=right:{\small$\{[0,v)\};1$}] at (0.3,6.4) {}; % N

@@

	% Numbers of extant ancestors and links, from top to bottom
	\node[label=right:{Extant material}] at (7.5, 8.2) {};
	\node[label=right:{2 \; $2 L - x - w$}] at (7.5, 7.6) {};
	\node[label=right:{4 \; $2 L + 2 v - x - w$}] at (7.5, 6.6) {};
	\node[label=right:{3 \; $2 L + v - w$}] at (7.5, 5.7) {};
	\node[label=right:{4 \; $2 L + x - v$}] at (7.5, 4.95) {};
	\node[label=right:{5 \; $2 L$}] at (7.5, 3.8) {};
	\node[label=right:{4 \; $2 L$}] at (7.5, 2.75) {};
	\node[label=right:{3 \; $2 L$}] at (7.5, 1.95) {};
	\node[label=right:{2 \; $2 L$}] at (7.5, 1.35) {};
	\node[label=right:{3 \; $3 L$}] at (7.5, 0.6) {};

	% Gray dashed lines to visually separate holding times
	\draw[color=gray, dashed] (7.5, 1.2) -- (11.1, 1.2); % D
	\draw[color=gray, dashed] (7.5, 1.5) -- (11.1, 1.5); % E and F
	\draw[color=gray, dashed] (7.5, 2.4) -- (11.1, 2.4); % G and H
	\draw[color=gray, dashed] (7.5, 3.1) -- (11.1, 3.1); % I and J
	\draw[color=gray, dashed] (7.5, 4.5) -- (11.1, 4.5); % K
	\draw[color=gray, dashed] (7.5, 5.4) -- (11.1, 5.4); % L
	\draw[color=gray, dashed] (7.5, 6) -- (11.1, 6); % M and N
	\draw[color=gray, dashed] (7.5, 7.2) -- (11.1, 7.2); % O
\end{tikzpicture}
&
\begin{tikzpicture}
	% Samples at x = 0, 4, and 6
	\node [circle, fill, scale=0.2,label=above right:{\small A}] at (0,0) {A};
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\node [circle, fill, scale=0.2,label=above right:{\small B}] at (4,0) {B};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\node [circle, fill, scale=0.2,label=above left:{\small C}] at (6,0) {C};
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);

	% B and C merge into D
	\draw (4,0) -- (4, 1.2) -- (6, 1.2) -- (6,0);
	\node [circle, fill, scale=0.2,label=above right:{\small D}] at (5,1.2) {D};
	\draw (4.6, 1) -- (5.4, 1) -- (5.4, 0.9) -- (4.6, 0.9) -- (4.6, 1);
	\draw (5.1, 1.1) -- (5.1, 0.8);
	\node [label=below:{\small $w$}] at (5.1, 1) {};

	% A splits into E and F
	\draw (0, 0) -- (0, 1.5) -- (-1,1.5) -- (1,1.5);
	\node [circle, fill, scale=0.2,label=above left:{\small E}] at (-1,1.5) {E};
	\draw (-1.4, 1.3) -- (-1.1, 1.3) -- (-1.1, 1.2) -- (-1.4, 1.2) -- (-1.4, 1.3);
	\draw (-1.1, 1.25) -- (-0.6, 1.25);
	\node [circle, fill, scale=0.2,label=above left:{\small F}] at (1,1.5) {F};
	\draw (0.6, 1.25) -- (0.9, 1.25);
	\draw (0.9, 1.3) -- (1.4, 1.3) -- (1.4, 1.2) -- (0.9, 1.2) -- (0.9, 1.3);
	\draw (1.2, 1.4) -- (1.2, 1.1);
	\node [label=below:{\small $x$}] at (1.2, 1.3) {};

	% D splits into G and H
	\draw (5, 1.2) -- (5, 2.4) -- (4,2.4) -- (6,2.4);
	\node [circle, fill, scale=0.2,label=above left:{\small G}] at (4,2.4) {G};
	\draw (3.6, 2.2) -- (4.1, 2.2) -- (4.1, 2.1) -- (3.6, 2.1) -- (3.6, 2.2);
	\draw (4.1, 2.15) -- (4.4, 2.15);
	\node [circle, fill, scale=0.2,label=above left:{\small H}] at (6,2.4) {H};
	\draw (5.6, 2.15) -- (6.1, 2.15);
	\draw (6.1, 2.2) -- (6.4, 2.2) -- (6.4, 2.1) -- (6.1, 2.1) -- (6.1, 2.2);
	\draw [color=red](5.8, 2.3) -- (5.8, 2.0);
	\node [label={[red]below:{\small $z$}}] at (5.8, 2.1) {};

	% F splits into I and J
	\draw (1, 1.5) -- (1, 3.1) -- (0,3.1) -- (2,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small I}] at (0,3.1) {I};
	\draw (-0.4, 2.85) -- (0.2, 2.85);
	\draw (0.2, 2.9) -- (0.4, 2.9) -- (0.4, 2.8) -- (0.2, 2.8) -- (0.2, 2.9);
	\node [circle, fill, scale=0.2,label=above left:{\small J}] at (2,3.1) {J};
	\draw (1.6, 2.85) -- (1.9, 2.85);
	\draw (1.9, 2.9) -- (2.2, 2.9) -- (2.2, 2.8) -- (1.9, 2.8) -- (1.9, 2.9);
	\draw (2.2, 2.85) -- (2.4, 2.85);

	% E and I merge into K
	\draw (-1, 1.5) -- (-1, 4.5) -- (0,4.5) -- (0,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small K}] at (-0.5,4.5) {K};
	\draw (-0.9, 4.3) -- (-0.6, 4.3) -- (-0.6, 4.2) -- (-0.9, 4.2) -- (-0.9, 4.3);
	\draw (-0.6, 4.25) -- (-0.3, 4.25);
	\draw (-0.3, 4.3) -- (-0.1, 4.3) -- (-0.1, 4.2) -- (-0.3, 4.2) -- (-0.3, 4.3);
	\draw (-0.5, 4.4) -- (-0.5, 4.1);
	\node [label=below:{\small $y$}] at (-0.5, 4.3) {};

	% H splits into P and Q. Red Q node drawn further down so that it overlays the black line underneath
	\draw (6, 2.4) -- (6, 3.8) -- (7, 3.8);
	\draw [color=red](6, 3.8) -- (5, 3.8);
	\node [color=red, circle, fill, scale=0.2,label={[red]above left:{\small P}}] at (5,3.8) {P};
	\draw (4.6, 3.55) -- (5.4, 3.55);
	\draw (6.6, 3.55) -- (7.1, 3.55);
	\draw (7.1, 3.6) -- (7.4, 3.6) -- (7.4, 3.5) -- (7.1, 3.5) -- (7.1, 3.6);

	% G and J merge into L
	\draw (4,2.4) -- (4,5.4) -- (2,5.4) -- (2,3.1);
	\node [circle, fill, scale=0.2,label=above left:{\small L}] at (3,5.4) {L};
	\draw (2.6, 5.2) -- (2.9, 5.2) -- (2.9, 5.1) -- (2.6, 5.1) -- (2.6, 5.2);
	\draw (2.9, 5.15) -- (3.4, 5.15);

	% K splits into M and N
	\draw (-0.5, 4.5) -- (-0.5, 6) -- (-1.5,6) -- (0.5,6);
	\node [circle, fill, scale=0.2,label=above left:{\small M}] at (-1.5,6) {M};
	\draw (-1.9, 5.75) -- (-1.3, 5.75);
	\draw (-1.3, 5.8) -- (-1.1, 5.8) -- (-1.1, 5.7) -- (-1.3, 5.7) -- (-1.3, 5.8);
	\node [circle, fill, scale=0.2,label=above left:{\small N}] at (0.5,6) {N};
	\draw (0.1, 5.8) -- (0.4, 5.8) -- (0.4, 5.7) -- (0.1, 5.7) -- (0.1, 5.8);
	\draw (0.4, 5.75) -- (0.9, 5.75);

	% P and L merge into R. R node drawn further down so that it overlays the black lines underneath
	\draw [color=red](5, 3.8) -- (5, 6.6) -- (4, 6.6);
	\draw (4,6.6) -- (3,6.6) -- (3, 5.4);
	\draw (3.6, 6.4) -- (3.9, 6.4) -- (3.9, 6.3) -- (3.6, 6.3) -- (3.6, 6.4);
	\draw (3.9, 6.35) -- (4.4, 6.35);

	% R and N merge into O. O node drawn further down so that it overlays the red line underneath
	\draw (0.5, 6) -- (0.5, 7.2) -- (4,7.2) -- (4,6.6);
	\draw (1.85, 6.95) -- (2.65, 6.95);
	% R node can now be added
	\node [color=red, circle, fill, scale=0.2,label={[red]above left:{\small R}}] at (4,6.6) {R};

	% M, O, and Q continue to the end
	\draw (-1.5, 6) -- (-1.5, 8);
	\draw [color=red](2.25, 7.2) -- (2.25, 8);
	\draw (7, 3.8) -- (7, 8);
	% O and Q nodes can now be added
	\node [circle, fill, scale=0.2,label=above left:{\small O}] at (2.25,7.2) {O};
	\node [color=red, circle, fill, scale=0.2,label={[red]above left:{\small Q}}] at (7,3.8) {Q};

>>>>

\section*{Introduction}
Inferring the genetic relationships between sampled genomes in the form of an
evolutionary tree is a necessary prerequisite for many analyses of species \citep{rannala2003genetics}, non (or
rarely) recombining sections of DNA \citep{cann1987mitochondrial,underhill2001annalsofhumangenetics} and viruses \citep{grenfell2004science}.
A genealogical tree captures what is known and
knowable about the genetic ancestry of the sample in an elegant and concise
way, by postulating a set of nodes that are ancestors common to the samples,
and the ancestral relationships between those nodes. A rich literature exists
on analysing the mathematical properties of these trees [cite?], and numerous
methods exist to infer them~\citep{felsenstein2004inferring}. The situation is
quite different in recombining organisms, where the analysis of genetic data
depends on summaries ultimately derived from the
trees~\citep{tajima1983evolutionary,tavare1984line}
such as allele frequencies and site frequency
spectra~\citep{achaz2009frequency,ralph2020efficiently},
patterns of linkage disequilibrium~\citep{mcvean2002genealogical}, and principal
components~\citep{mcvean2009genealogical}. Genealogical analysis is equally
fundamental to the study of recombining organisms, but profound technical
difficulties have made the routine inference of recombinant genealogies
impossible, and therefore tree-based analysis methods have been largely
unavailable to the fields of population and statistical
genetics.

@@

In this paper we [turn into proper round up paragraph later]
\begin{enumerate}
\item Discuss the classical Ancestral Recombination Graph formulation,
and show how it derives from (and is limited by) the coalescent with
recombination.
\item Suggest a definition of ARGs that is free of these limitations,
where the formulation is derived from a (normally diploid) pedigree rather than from
coalescent approximations, and where the genetic
material which is transmitted is described by annotations attached to
edges rather than nodes.
\item Suggest a classification of ARG nodes that helps us to understand
the properties of the structures inferred by different methods, and illustrate
with some examples.
% Perhaps we should also mention something about simplification and unknowable
% nodes, e.g. "show how some of the nodes are not required for useful interpretation
% of ancestry".
\end{enumerate}

@@

\begin{figure}[ht]
\centering
% FIXME this is a quick nasty hack to make the figure a bit smaller and
% prevent flushing all the other figures to the end of the document.
\scalebox{0.5}{
\begin{tabular}{cc}
\begin{tikzpicture}
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);

	\draw (4,0) -- (4, 1.2) -- (6, 1.2) -- (6,0);
	\draw (4.6, 1) -- (5.4, 1) -- (5.4, 0.9) -- (4.6, 0.9) -- (4.6, 1);
	\draw (5.1, 1.1) -- (5.1, 0.8);
	\node [label=below:{\small $w$}] at (5.1, 1) {};

	\draw (0, 0) -- (0, 1.5) -- (-1,1.5) -- (1,1.5);
	\draw (-1.4, 1.3) -- (-1.1, 1.3) -- (-1.1, 1.2) -- (-1.4, 1.2) -- (-1.4, 1.3);
	\draw (-1.1, 1.25) -- (-0.6, 1.25);
	\draw (0.6, 1.25) -- (0.9, 1.25);
	\draw (0.9, 1.3) -- (1.4, 1.3) -- (1.4, 1.2) -- (0.9, 1.2) -- (0.9, 1.3);
	\draw (1.2, 1.4) -- (1.2, 1.1);
	\node [label=below:{\small $x$}] at (1.2, 1.3) {};

	\draw (5, 1.2) -- (5, 2.4) -- (4,2.4) -- (6,2.4);
	\draw (3.6, 2.2) -- (4.1, 2.2) -- (4.1, 2.1) -- (3.6, 2.1) -- (3.6, 2.2);
	\draw (4.1, 2.15) -- (4.4, 2.15);
	\draw (5.6, 2.15) -- (6.1, 2.15);
	\draw (6.1, 2.2) -- (6.4, 2.2) -- (6.4, 2.1) -- (6.1, 2.1) -- (6.1, 2.2);

	\draw (1, 1.5) -- (1, 3.1) -- (0,3.1) -- (2,3.1);
	\draw (-0.4, 2.85) -- (0.2, 2.85);
	\draw (0.2, 2.9) -- (0.4, 2.9) -- (0.4, 2.8) -- (0.2, 2.8) -- (0.2, 2.9);
	\draw (1.6, 2.85) -- (1.9, 2.85);
	\draw (1.9, 2.9) -- (2.2, 2.9) -- (2.2, 2.8) -- (1.9, 2.8) -- (1.9, 2.9);
	\draw (2.2, 2.85) -- (2.4, 2.85);

	\draw (-1, 1.5) -- (-1, 4.5) -- (0,4.5) -- (0,3.1);
	\node [scale=0.2,label=above left:{\small A}] at (-0.5,4.5) {A};
	\draw (-0.9, 4.3) -- (-0.6, 4.3) -- (-0.6, 4.2) -- (-0.9, 4.2) -- (-0.9, 4.3);
	\draw (-0.6, 4.25) -- (-0.3, 4.25);
	\draw (-0.3, 4.3) -- (-0.1, 4.3) -- (-0.1, 4.2) -- (-0.3, 4.2) -- (-0.3, 4.3);
	\draw (-0.5, 4.4) -- (-0.5, 4.1);
	\node [label=below:{\small $y$}] at (-0.5, 4.3) {};

	\draw (4,2.4) -- (4,5.4) -- (2,5.4) -- (2,3.1);
	\node [scale=0.2,label=above left:{\small B}] at (3,5.4) {B};
	\draw (2.6, 5.2) -- (2.9, 5.2) -- (2.9, 5.1) -- (2.6, 5.1) -- (2.6, 5.2);
	\draw (2.9, 5.15) -- (3.4, 5.15);

	\draw (-0.5, 4.5) -- (-0.5, 6) -- (-1.5,6) -- (0.5,6);
	\draw (-1.9, 5.75) -- (-1.3, 5.75);
	\draw (-1.3, 5.8) -- (-1.1, 5.8) -- (-1.1, 5.7) -- (-1.3, 5.7) -- (-1.3, 5.8);
	\draw (0.1, 5.8) -- (0.4, 5.8) -- (0.4, 5.7) -- (0.1, 5.7) -- (0.1, 5.8);
	\draw (0.4, 5.75) -- (0.9, 5.75);

	\draw (0.5, 6) -- (0.5, 7.2) -- (3,7.2) -- (3,5.4);
	\node [scale=0.2,label=above:{\small C}] at (1.75,7.2) {C};
	\draw (1.35, 6.95) -- (2.15, 6.95);

	\draw (-1.5, 6) -- (-1.5, 8);
	\draw (6, 2.4) -- (6, 8);

	% Edge annotations above each event
	\node [label=left:{\small$\{[0,L)\};1$}] at (0.2,0.6) {}; 
	\node [label=left:{\small$\{[0,L)\};1$}] at (4.2,0.4) {}; 
	\node [label=right:{\small$\{[0,L)\};1$}] at (5.8,0.4) {}; 
	\node [label=left:{\small$\{[0,L)\};2$}] at (5.2,1.6) {}; 
	\node [label=left:{\small$\{[0,v)\};1$}] at (-0.8,2.3) {}; 
	\node [label=right:{\small$\{[v,L)\};1$}] at (0.8,2.1) {}; 
	\node [label=right:{\small$\{[0,w)\};2$}] at (3.8,3.9) {}; 
	\node [label=left:{\small$\{[w,L)\};2$}] at (6.2,5) {}; 
	\node [label=right:{\small$\{[x,L)\};1$}] at (-0.2,3.8) {}; 
	\node [label=right:{\small$\{[v,x)\};1$}] at (1.8,4.1) {}; 
	\node [label=left:{\small$\{[0,v), [x, L)\};1$}] at (-0.3,5.2) {}; 
	\node [label=right:{\small$\{[0,v)\};2$}] at (2.8,6.4) {};
	\node [label=left:{\small$\{[x,L)\};1$}] at (-1.3,7) {};
	\node [label=right:{\small$\{[0,v)\};1$}] at (0.3,6.4) {};

@@

	% Numbers of extant ancestors and links, from top to bottom
	\node[label=right:{CA \; RE}] at (7.5, 8.2) {};
	\node[label=right:{$\binom{2}{2}$ \; $(2 L - x - w) \rho$}] at (7.5, 7.6) {};
	\node[label=right:{$\binom{4}{2}$ \; $(2 L + 2 v - x - w) \rho$}] at (7.5, 6.6) {};
	\node[label=right:{$\binom{3}{2}$ \; $(2 L + v - w) \rho$}] at (7.5, 5.7) {};
	\node[label=right:{$\binom{4}{2}$ \; $(2 L + x - v) \rho$}] at (7.5, 4.95) {};
	\node[label=right:{$\binom{5}{2}$ \; $2 L \rho$}] at (7.5, 3.8) {};
	\node[label=right:{$\binom{4}{2}$ \; $2 L \rho$}] at (7.5, 2.75) {};
	\node[label=right:{$\binom{3}{2}$ \; $2 L \rho$}] at (7.5, 1.95) {};
	\node[label=right:{$\binom{2}{2}$ \; $2 L \rho$}] at (7.5, 1.35) {};
	\node[label=right:{$\binom{3}{2}$ \; $3 L \rho$}] at (7.5, 0.6) {};

	% Gray dashed lines to visually separate holding times
	\draw[color=gray, dashed] (7.5, 1.2) -- (11.1, 1.2);
	\draw[color=gray, dashed] (7.5, 1.5) -- (11.1, 1.5);
	\draw[color=gray, dashed] (7.5, 2.4) -- (11.1, 2.4);
	\draw[color=gray, dashed] (7.5, 3.1) -- (11.1, 3.1);
	\draw[color=gray, dashed] (7.5, 4.5) -- (11.1, 4.5);
	\draw[color=gray, dashed] (7.5, 5.4) -- (11.1, 5.4);
	\draw[color=gray, dashed] (7.5, 6) -- (11.1, 6);
	\draw[color=gray, dashed] (7.5, 7.2) -- (11.1, 7.2);
\end{tikzpicture}
&
\begin{tikzpicture}
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);

	\draw (4,0) -- (4, 1.2) -- (6, 1.2) -- (6,0);
	\draw (4.6, 1) -- (5.4, 1) -- (5.4, 0.9) -- (4.6, 0.9) -- (4.6, 1);
	\draw (5.1, 1.1) -- (5.1, 0.8);
	\node [label=below:{\small $w$}] at (5.1, 1) {};

	\draw (0, 0) -- (0, 1.5) -- (-1,1.5) -- (1,1.5);
	\draw (-1.4, 1.3) -- (-1.1, 1.3) -- (-1.1, 1.2) -- (-1.4, 1.2) -- (-1.4, 1.3);
	\draw (-1.1, 1.25) -- (-0.6, 1.25);
	\draw (0.6, 1.25) -- (0.9, 1.25);
	\draw (0.9, 1.3) -- (1.4, 1.3) -- (1.4, 1.2) -- (0.9, 1.2) -- (0.9, 1.3);
	\draw (1.2, 1.4) -- (1.2, 1.1);
	\node [label=below:{\small $x$}] at (1.2, 1.3) {};

	\draw (5, 1.2) -- (5, 2.4) -- (4,2.4) -- (6,2.4);
	\draw (3.6, 2.2) -- (4.1, 2.2) -- (4.1, 2.1) -- (3.6, 2.1) -- (3.6, 2.2);
	\draw (4.1, 2.15) -- (4.4, 2.15);
	\draw (5.6, 2.15) -- (6.1, 2.15);
	\draw (6.1, 2.2) -- (6.4, 2.2) -- (6.4, 2.1) -- (6.1, 2.1) -- (6.1, 2.2);
	\draw [color=red](5.8, 2.3) -- (5.8, 2.0);
	\node [label={[red]below:{\small $z$}}] at (5.8, 2.1) {};

	\draw (1, 1.5) -- (1, 3.1) -- (0,3.1) -- (2,3.1);
	\draw (-0.4, 2.85) -- (0.2, 2.85);
	\draw (0.2, 2.9) -- (0.4, 2.9) -- (0.4, 2.8) -- (0.2, 2.8) -- (0.2, 2.9);
	\draw (1.6, 2.85) -- (1.9, 2.85);
	\draw (1.9, 2.9) -- (2.2, 2.9) -- (2.2, 2.8) -- (1.9, 2.8) -- (1.9, 2.9);
	\draw (2.2, 2.85) -- (2.4, 2.85);

	\draw (-1, 1.5) -- (-1, 4.5) -- (0,4.5) -- (0,3.1);
	\draw (-0.9, 4.3) -- (-0.6, 4.3) -- (-0.6, 4.2) -- (-0.9, 4.2) -- (-0.9, 4.3);
	\draw (-0.6, 4.25) -- (-0.3, 4.25);
	\draw (-0.3, 4.3) -- (-0.1, 4.3) -- (-0.1, 4.2) -- (-0.3, 4.2) -- (-0.3, 4.3);
	\draw (-0.5, 4.4) -- (-0.5, 4.1);
	\node [label=below:{\small $y$}] at (-0.5, 4.3) {};

	\draw (6, 2.4) -- (6, 3.8) -- (7, 3.8);
	\draw [color=red](6, 3.8) -- (5, 3.8);
	\draw (4.6, 3.55) -- (5.4, 3.55);
	\draw (6.6, 3.55) -- (7.1, 3.55);
	\draw (7.1, 3.6) -- (7.4, 3.6) -- (7.4, 3.5) -- (7.1, 3.5) -- (7.1, 3.6);

	\draw (4,2.4) -- (4,5.4) -- (2,5.4) -- (2,3.1);
	\draw (2.6, 5.2) -- (2.9, 5.2) -- (2.9, 5.1) -- (2.6, 5.1) -- (2.6, 5.2);
	\draw (2.9, 5.15) -- (3.4, 5.15);

	\draw (-0.5, 4.5) -- (-0.5, 6) -- (-1.5,6) -- (0.5,6);
	\draw (-1.9, 5.75) -- (-1.3, 5.75);
	\draw (-1.3, 5.8) -- (-1.1, 5.8) -- (-1.1, 5.7) -- (-1.3, 5.7) -- (-1.3, 5.8);
	\draw (0.1, 5.8) -- (0.4, 5.8) -- (0.4, 5.7) -- (0.1, 5.7) -- (0.1, 5.8);
	\draw (0.4, 5.75) -- (0.9, 5.75);

	\draw [color=red](5, 3.8) -- (5, 6.6) -- (4, 6.6);
	\draw (4,6.6) -- (3,6.6) -- (3, 5.4);
	\draw (3.6, 6.4) -- (3.9, 6.4) -- (3.9, 6.3) -- (3.6, 6.3) -- (3.6, 6.4);
	\draw (3.9, 6.35) -- (4.4, 6.35);

	\draw (0.5, 6) -- (0.5, 7.2) -- (4,7.2) -- (4,6.6);
	\draw (1.85, 6.95) -- (2.65, 6.95);

	\draw (-1.5, 6) -- (-1.5, 8);
	\draw [color=red](2.25, 7.2) -- (2.25, 8);
	\draw (7, 3.8) -- (7, 8);
